Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-20 prop_iop.tex
fixed intro

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\midd}{{\mbox{\wesa{middle}}}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\minus}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}

@@

>>>>

\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}
\newcommand{\midd}{{\mbox{\wesa{middle}}}}
\newcommand{\ket}[1]{{\left\vert{#1}\right\rangle}}
\newcommand{\fket}[1]{{|#1\rangle}}
\newcommand{\fproj}[1]{|#1\rangle\langle #1|}
\newcommand{\op}[2]{\ensuremath{\left\vert{#1}\middle\rangle\middle\langle{#2}\right\vert}}
\newcommand{\proj}[1]{\op{#1}{#1}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\minus}{\texttt{-}}
\newcommand{\ip}[2]{\ensuremath{\left\langle{#1}\middle\vert{#2}\right\rangle}}

@@

Textbook quantum mechanics asserts that, given a quantum spin system
described by the wavefunction
$\ket{\psi}=\frac{\sqrt{\pi}}{2}\fket{\ps\frac{1}{2}}+\frac{\sqrt{4-\pi}}{2}\fket{\minus\frac{1}{2}}$
and the observable $S_z = \frac{\hbar}{2}(\fproj{\ps\frac{1}{2}}-\fproj{\minus\frac{1}{2}})$,
the probability of observing the eigenvalue $\ps\frac{\hbar}{2}$ (with
post-measurement state $\fket{\ps\frac{1}{2}}$) is $\frac{\pi}{4}$ and
the probability of observing $\minus\frac{\hbar}{2}$ (with post-measurement
state $\fket{\minus\frac{1}{2}}$) is $1-\frac{\pi}{4}$. According to the
frequency interpretation of probability, the above assertion implies
that when performing a very large number of experiments on quantum
systems described by wavefunction $\ket{\psi}$, a fraction
$\frac{\pi}{4}$ of the experiments will result in the observation
$\ps\frac{\hbar}{2}$ and the remaining fraction $1-\frac{\pi}{4}$ will
result in the observation $\fket{\minus\frac{1}{2}}$.

In reality, i.e., in an actual experiment, simulation, or computation,
bounded by space, time, and energy resources, the situation is much
fuzzier: (i) we cannot \emph{exactly} prepare the state $\psi$; (ii)
we cannot \emph{exactly} build a measurement apparatus corresponding
to observable $S_z$; and (iii) we cannot prepare \emph{exact} replicas
of any state. In other words, we can only perform a limited number of
experiments on quantum systems closely related to wavefunction
$\ket{\psi}$ and using an apparatus that closely approximates
observable $S_z$. Given any fixed resources, these experiments will
\emph{not} result in the \emph{exact} fraction $\frac{\pi}{4}$ of
observations $\ps\frac{\hbar}{2}$ and $1-\frac{\pi}{4}$ of observations
$\minus\frac{\hbar}{2}$. Indeed, the state of the art algorithms for
computing the $n$th binary digit of~$\pi$ require on the order of
$O\left(n\log^{O\left(1\right)}\left(n\right)\right)$
operations~\cite{journals/moc/BaileyBP97} which means that simply
referring to the $n$th digit of $\pi$ requires more and more resources
as~$n$ gets larger.

All of this is well-known and holds in both the classical and quantum
world. In the classical world, these observations are believed to be
well-understood approximations to an idealized reality. The question
in the quantum world is more subtle and it is not evident at all that
it does not alter the very foundations of quantum mechanics. Indeed
taking such resource bounds into consideration is what founded
computer science as a discipline and has become crucial for
understanding the very nature of computation. Following
Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective is
also crucial for understanding the very nature of physical processes.

In previous work, \ldots

\newpage
